---
title: "Clinical Pathway for Assessment of Resuscitation Status and Limitation of Therapy for Hospitalised Medical Patients"
description: 
  A consensus statement commissioned by Advanced Acute Internal Medicine Society Malaysia.
author:
  - name: Dr Saiful Safuan Md Sani 
    url: https://saifulsafuan.com
    affiliation: Advanced Acute Internal Medicine Society Malaysia & Department of Medicine Hospital Kuala Lumpur
    affiliation_url: https://aaims.co
date: "`r Sys.Date()`"
output: 
  distill::distill_article:
    self_contained: yes
    toc: yes
    toc_depth: 2
---


```{r message=FALSE, echo=FALSE, warning=FALSE}
library(distill)
library(knitr)
```
```{r}
staplr::split_pdf("cplimit.pdf", output_directory = ".", prefix = "cplimit_")
```
```{r label, out.width = "85%", fig.cap = c("Pathway page 1", "Pathway page 2", "Introduction", "Assessment for resuscitation status", "SOFA Score Table", "Clinical Frailty Scale Table", "Direction of Care", "Withdrawal of therapy", "Symptom Management at the End of Life", "References", "Consensus Development Group"), echo = FALSE}
flist <- list.files()
cplimit_files <- flist[grep("cplimit_", flist)]

```
## Introduction
```{r, out.width = "85%", fig.cap = "Introduction", echo = FALSE}
knitr::include_graphics("cplimit_0003.pdf")
```
<a href="#top">Return to table of contents</a>

## Assessment for resuscitation status
```{r, out.width = "85%", fig.cap = "Assessment for resuscitation status", echo = FALSE}
knitr::include_graphics("cplimit_0004.pdf")
```
<a href="#top">Return to table of contents</a>

## SOFA Score Table
```{r, out.width = "85%", fig.cap = "SOFA Score Table", echo = FALSE}
knitr::include_graphics("cplimit_0005.pdf")
```
<a href="#top">Return to table of contents</a>

## Clinical Frailty Scale Table
```{r, out.width = "85%", fig.cap = "Clinical Frailty Scale Tabl", echo = FALSE}
knitr::include_graphics("cplimit_0006.pdf")
```
<a href="#top">Return to table of contents</a>

## Direction of Care
```{r, out.width = "85%", fig.cap = "Direction of Care", echo = FALSE}
knitr::include_graphics("cplimit_0007.pdf")
```
<a href="#top">Return to table of contents</a>

## Withdrawal of therapy
```{r, out.width = "85%", fig.cap = "Withdrawal of therapy", echo = FALSE}
knitr::include_graphics("cplimit_0008.pdf")
```
<a href="#top">Return to table of contents</a>

## Symptom Management at the End of Life
```{r, out.width = "85%", fig.cap = "Symptom Management at the End of Life", echo = FALSE}
knitr::include_graphics("cplimit_0009.pdf")
```
<a href="#top">Return to table of contents</a>

## References
```{r, out.width = "85%", fig.cap = "References", echo = FALSE}
knitr::include_graphics("cplimit_0010.pdf")
```
<a href="#top">Return to table of contents</a>

## Pathway page 1
```{r, out.width = "85%", fig.cap = "Pathway page 1", echo = FALSE}
knitr::include_graphics("cplimit_0001.pdf")
```
<a href="#top">Return to table of contents</a>

## Pathway page 2
```{r, out.width = "85%", fig.cap = "Pathway page 2", echo = FALSE}
knitr::include_graphics("cplimit_0002.pdf")
```
<a href="#top">Return to table of contents</a>

## Consensus Development Group
```{r, out.width = "85%", fig.cap = "Consensus Development Group", echo = FALSE}
knitr::include_graphics("cplimit_0011.pdf")
```
<a href="#top">Return to table of contents</a>