---
title: "Epidemic Curve of COVID-19 New Cases"
description: 
  Epidemic Curve with Moving Averages on New Cases
author:
  - name: Dr Saiful Safuan Md Sani 
    url: https://saifulsafuan.com
    affiliation: Advanced Acute Internal Medicine Society Malaysia & Department of Medicine Hospital Kuala Lumpur
    affiliation_url: https://aaims.co
date: "`2020-04-12`"
output: 
  distill::distill_article:
    self_contained: yes
    toc: yes
    toc_depth: 2
---
### "To bring the pandemic to an end countries have to bend the curve – they have to achieve a plateau then decline in the number of daily cases." - [Our World in Data](https://ourworldindata.org/coronavirus#are-countries-bending-the-curve) 

### ***The chart below illustrates that a 10-day period is the best time frame to use to decide on the effectiveness of the MCO strategy in Malaysia.***

```{r message=FALSE, echo=FALSE}
library(plotly)
library(shiny)
library(googlesheets)
library(gsheet)
```
```{r warning=FALSE, message=FALSE, echo=FALSE}
url <- 'docs.google.com/spreadsheets/d/1jLn3UoJBfusBcEbLS8n8oPBJd6bUiA0WMqZ7LHNkdjw/edit?usp=sharing'
data <- gsheet2tbl(url)
```

```{r fig.width=10, fig.height=6, echo=FALSE, warning=FALSE, message=FALSE}
p <- plot_ly(data, x = ~date, y = ~dailynew, type = 'bar', name = 'New cases confirmed each day',
        marker = list(color = 'rgb(55, 83, 109)')) %>%
  add_trace(y = ~SMA10, name = '10-day Moving averages', mode = "lines", type = "scatter", marker = list(color = 'rgb(255,125,0)')) %>%
  add_trace(y = ~SMA5, name = '5-day Moving averages', mode = "lines", line = list(color = 'rgb(255,223,0)'), type = "scatter", marker = list(color = 'rgb(255,223,0)')) %>%
  
  layout(title = 'New cases confirmed each day',
         xaxis = list(
           title = "",
           tickformat = "%b %d",
           tickfont = list(
             size = 14,
             color = 'rgb(107, 107, 107)')),
         yaxis = list(
           title = 'Confirmed new cases',
           titlefont = list(
             size = 16,
             color = 'rgb(107, 107, 107)'),
           tickfont = list(
             size = 14,
             color = 'rgb(107, 107, 107)')),
         legend = list(x = 0, y = 1, bgcolor = 'rgba(255, 255, 255, 0)', bordercolor = 'rgba(255, 255, 255, 0)'),
         barmode = 'group', bargap = 0.15, bargroupgap = 0.1)
p
```
The 10-day moving averages curve is more 'stable' or less erratic compared to the 5-day moving averages curve.
